Predicting computational reproducibility of scientific pipelines using collaborative filtering

### 2018-05-07 paper.tex
Just for Test
Added ALS-Bias figures

As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.

\subsubsection{RFNT-L}
Figure~\ref{fig:ALS-Succeed}

\subsubsection{RFNT-S}
Figure~\ref{fig:ALS-Succeed}

>>>>

% ALS-RFNT approaches
As it mentioned earlier, for $\alpha < \nicefrac{1}{3}$ RFNT approaches are not applicable, 
therefor for training ratio less than $0.4$ RFNU method is employed. As a result, in terms of 
evaluating the performance of RFNT-L and RFNT-S approches, only those accuracy results are 
considered which their training set are equal or geather than 0.4 percent of the whole utility matrix.

\subsubsection{RFNT-L}
In Figure~\ref{fig:ALS-Succeed}, the results show that RFNT-L performance is always more accurate than
dummy classifier even in its lowest accuracy value observed at training ratio of $0.6$ in C5C6 ($0.78$ percent).
Dispite of this sudden mentioned drop to $78\%$ accuracy, RFNT-L method has slight growing trend throughout the 
increment of training ratio and its accuracy is always more than $90\%$.

\subsubsection{RFNT-S}
Figure~\ref{fig:ALS-Succeed} shows the overall performance of RFNT-S methods in three different condition pairs.
Similar to RFNT-L, this method also has constant accuracy increament with maximum less accuracy of 0.07 than 
Random Unreal method throughout the experiment of C5C7 and C6C7.

\subsection{Adding biases}
In this phase of experiment, the variation in values of utility matrix which caused by subjects and files are also considered. 
Figure~\ref{fig:ALS-Bias-PFS} presents the result of three methods of RFNU, RFNT-L and RFNT-S with having a comparison with
Random Unreal method.

\begin{figure}[h!]
        \centering
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs6-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-5vs7-PFS}
        \end{subfigure}
        \begin{subfigure}[b]{0.8\linewidth}
                \includegraphics[width=\columnwidth]{figures/ALS-Bias/ALS-Bias-6vs7-PFS}
        \end{subfigure}
        \caption{Average performance of random methods in three different condition pairs with cosidering Bias of both subjects and files}
        \label{fig:ALS-Bias-PFS}
\end{figure}
